DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/evaluation.tex
Minor changes

In this experiment, we launch multiple instances of DeepPicar's CNN
model at the same time and measure its impact on their inference
timings. In other words, we are interested in how shared resource
contention affects inference timing. These instances are not identical
copies of the same model, but are instead copies of different models
(but of the same network architecture). 
This is done to ensure that no L2 cache memory is shared between the 
models as they are running.

>>>>

In this experiment, we launch multiple instances of DeepPicar's CNN
model at the same time and measure its impact on their inference
timings. In other words, we are interested in how shared resource
contention affects inference timing. For this, we create four different
neural network models, that have the same network architecture, and
run them simultaneously.
%% These instances are not identical
%% copies of the same model, but are instead copies of different models
%% (but of the same network architecture). 
%% This is done to ensure that no L2 cache memory is shared between the 
%% models as they are running.
